Why Donors Donate?

### 2020-09-10 analysis/05_market_simulator.Rmd
Last changes to inputs

                        "Highschool graduate", 

@@

                        "2 year college",
                        "4 year college",
                        "Graduate or orofessional degree",

@@

# Need to Check on Hold out
selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

@@

# Need to check hold out 
selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Never",
                     "Rarely",
                     "At least once a month"))

@@

# Need to check hold out level
selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Hold out",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

# Need to check hold out level
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

# Need to check hold out level
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Rarely',
                     'Atleast once a month'))

@@

# Need to Change the Inputs
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

# Need to check hold out level
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

@@

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than highschool",
                     "Highschool graduate",
                     "Some college",
                     "2 year college",
                     "4 year college",
                     "Graduate or professional degree",
                     "Doctorate"))

>>>>

                        "High school graduate", 

@@

                        "2 year degree",
                        "4 year degree",
                        "Graduate or professional degree",

@@

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"))

@@

selectInput("p1_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely",
                     "At least once a month"))

@@

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"))

selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all",
                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust"))

selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('More than once a month, less than once a year',
                     'Atleast once a month'))

@@

selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("No", "Yes"))

selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely",
                     "More than once a month, less than once a year",
                     "At least once a month"))

@@

selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"))
